Demystifying the Computer Science Ph.D. Admission in the US

### 2023-06-09 phd-cs-us.tex
updates csrankings table

Sometime a faculty wants to interview an applicant to make a decision. Typically this means they lean toward admitting you (if we don't like your application, we will not bother doing the interview).

@@

\begin{tcolorbox}[left=1pt,right=1pt,top=1pt,bottom=1pt]
Vu: At GMU, we are encouraged to interview candidates. For very strong candidates, the interview is actually to recruit them.  In some rare cases a faculty interviews a candidate that they see potentials and want argue for admission, i.e., without the interview, that candidate is definitely rejected. In any case, getting interview means you have a very good chance of being admitted.
\end{tcolorbox}

@@

\begin{table}
  \centering
  \caption{Different types of PhD funding}\label{tab:funding}
  \begin{tabular}{c|c|c|c}
    \toprule
    &\textbf{TA}&\textbf{RA}&\textbf{Fellowship}\\
    \midrule
    \textbf{From} & School & Profs. & School/External\\
    \textbf{For}                  & Teaching Assistant       & Research                        & Research                              \\
    \textbf{Tuition/Ins./Stipend} & Yes                      & Yes                             & Yes                                   \\
    \textbf{Cover Summer?}              & No                       & Maybe                           & Yes                                   \\
    \midrule
    \textbf{Pros}                 & Research Freedom         & Get to do research              & Research Freedom                      \\
    \textbf{Cons}                 & TA, Uncertain            & Research restriction, Uncertain & Competitive, limited             \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

Sometime a faculty wants to interview an applicant to make a decision. This means they are leaning toward admitting you (if we don't like your application, we will not bother doing the interview).

@@

\begin{tcolorbox}[left=1pt,right=1pt,top=1pt,bottom=1pt]
Vu: At GMU, we are encouraged to interview candidates. For very strong candidates, the interview is actually to recruit them.  In some cases a faculty interviews a candidate that they see potentials and wants argue for admission, i.e., without the interview, that candidate is definitely rejected. In any case, getting interview means you have a very good chance of being admitted.
\end{tcolorbox}

@@

\begin{table}
  \centering
  \footnotesize
  \caption{Different types of PhD funding}\label{tab:funding}
  \begin{tabular}{c|c|c|c}
    \toprule
    &\textbf{TA}&\textbf{RA}&\textbf{Fellowship}\\
    \midrule
    \textbf{From} & School & Profs. & School/External\\
    \textbf{For}                  & Teaching Assistant       & Research                        & Research                              \\
    \textbf{Tuition/Ins./Stipend} & Yes                      & Yes                             & Yes                                   \\
    \textbf{Cover Summer?}              & No                       & Maybe                           & Yes                                   \\
    \midrule
    \textbf{Pros}                 & Research Freedom         & Get to do research              & Research Freedom                      \\
    \textbf{Cons}                 & TA, Uncertain            & Research restriction, Uncertain & Competitive, limited             \\
    \bottomrule
  \end{tabular}
\end{table}
